The sweet spot for local polygenic adaptation: a case study motivated by stickleback

### 2018-09-12 Stickleback_Paper.tex
subplot captions

\begin{figure}
	\begin{center}
  		\includegraphics[width=1.0\linewidth]{semi_final_plots/Fst_semi_final.png}
  		\caption{
		$F_{st}$ as a function of genomic location between all combinations of the three subpopulations; 
		the old lakes, the new lakes, and the marine.
		$F_{st}$ was calculated based upon allele frequencies in genomic windows of 500 mb. 
		The four columns of subplot represent separate simulations with increasing $m$. 
		The three rows represent the combinations of the three separate populations.
		Ten vertical dotted pink lines in each subplot represent regions which have the potential to affect phenotype
		 }
  		\label{fig:Fst}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{semi_final_plots/FAA_semi_final.png}
  		\caption{
		Distribution of freshwater adapted alleles 
		}
		\label{fig:MPFAI}
	\end{center}
\end{figure}

>>>>

\begin{figure}
	\begin{center}
  		\includegraphics[width=1.0\linewidth]{semi_final_plots/Fst_semi_final.png}
  		\caption{
		$F_{st}$ as a function of genomic location between all combinations of the three subpopulations; 
		the old lakes, the new lakes, and the marine.
		$F_{st}$ was calculated based upon allele frequencies in genomic windows of 500 mb. 
		The four columns of subplots are separate simulations with increasing $m$. 
		The three rows are the combinations of the three separate populations.
		Ten vertical dotted pink lines in each subplot represent regions which have the potential to affect phenotype
		 }
  		\label{fig:Fst}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{semi_final_plots/FAA_semi_final.png}
  		\caption{
		Distribution of freshwater adapted alleles among the three populations. 
		A freshwater adapted variant is defined as, at any generation throughout the simulation,
		a variant affecting phenotype that is greater than 0.5 frequency in any of the old lakes, 
		and less than 0.5 frequency in the marine population. 
		Subplot $A$ is the distribution throughout the simulation, of the mean number of
		freshwater adapted variants per individual, in each population.
		Subplot $B$ is the distribution throughout the simulation, of the mean \emph{percentage} of
		freshwater adapted variants per individual, in each population. 
		Subplot $C$ is the distribution throughout the simulation, of the total number of
		freshwater adapted alleles defined at any one generation.
		In other words, $B  =  A  /  C$.
		}
		\label{fig:MPFAI}
	\end{center}
\end{figure}
